Dynein project log

### 2016-12-17 thesis_stuff/thesis_stuff.tex
Add better calculations ftions for binding rate from Sarlah paper, and a script to help in this calculation

\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\pagestyle{fancy}
\fancyhf{}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example footer:
%\rfoot{\color{headings} {\sffamily Last update: \today}. Typeset with Xe\LaTeX}

@@

>>>>

\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{verbatim}
\pagestyle{fancy}
\fancyhf{}

@@

\subsection{Properly implementing binding rates}
To determine if it is time to do a state transition, we calculate the per-timestep
transition probability $k_b/dt$, pick a number between zero and one, and transition
if our number was the lower of the two.\\

One issue with this is the rate constant $k_b$ is calculated experimentally from an
ensemble of dynein, and doesn't take into account how transitions are much more likely in some orientations than others. In reality, dynein will only bind to the MT when
its binding domain is less than 0.2nm away from a binding site.\\

To fix this, we define a parameter $n$, the time fraction onebound dynein is capable
of binding. Then a weighted average of the bindable and non-bindable rate constants
looks like:

\begin{equation*}
  nk_{bindable} + (n-1)k_{nonbindable} = k_b
\end{equation*}

Since we say $k_{nonbindable} = 0$, $k_{bindable}$, our effective rate constant of
binding, is $k_b/n$. Thus our preexponential Arrenhius factor is (see above):

\begin{equation*}
  B = \frac{k_{b}}{n\sqrt{e}}
\end{equation*}

\subsubsection{Calculating $n$}
A script, \verb|simulations/get_binding_time_fraction.py|, calculates how often
a onebound dynein spends in a bindable state:

\verbatiminput{../simulations/simulation_results/binding_time_fraction.txt}
